### 2015-06-29 narrative/intro.tex
polishing intro

We will examine the research challenges from the perspective of
%
(1) the user of the system who is attempting to run an exascale simulation,
%
(2) the Storage System and I/O layer which needs to negotiate between all of
the users, and finally
%
(3) the user of the system who is attempting to understand the data which
was produced from a set of simulations.

\subsection{Writing Perspective}
\label{subsec:sim-perspective}
From the perspective of the simulation scientist, they want to be able to
have knowledge about how much time they will put into writing their data,
and how much storage space they will be able to get during the lifetime of
their simulations. Furthermore, they would like the ability to get a certain
amount of Quality of Service such that they can then make decisions when the
expected bandwidth, for example, is less than what they desire. The user will
then place in a certain set of rules which the system can make autonomic
decisions to help decide what should be done.
%

One of the key aspects of our approach is to allow the users to define the
utility (importance) of their data; in other-words, for each data object, users
need to come up with a way to define pieces of the object which have more
utility (more importance) . There are many clear research challenges faced with
this approach including: 1) How do we make this simple enough so that users can
do this, 2) can we come up with a model to allow the system to then make the
autonomic decisions to save the data which has the highest utility, and 3) can
we allow the back-end storage system to interact with this definition so that
it can optimize not just over one application but across all of the
applications.
 %
  In our simple scenario, a user wants to perhaps write 1 PB of data every hour
for their checkpoint/restart, and they which to write 500TB of data every 15
minutes for their analysis and visualization results which have been reduced by
using in situ reduction techniques. At this stage, they will ask the system to
write their data, and they would like to get an estimated time which they can
then figure out, through a series of rules, whether they want to write out all
of the data or if they want to write none of the data but rather wait for a
later time to write or write a reduced amount of data, along with some code
container to allow them to regenerate the data with a certain level of
accuracy.  Furthermore, they realize that the analysis data will be saved on
either the parallel file system, or the campaign storage, a longer term storage
area with lower bandwidth than the parallel file system, or if some of the data
will just go to tape. Each piece of data the user will specify the lifetime so
that the data with the most important utility is kept around for the longest
period of time, but the data which has the least utility might be migrated to
lower layers of the storage hierarchy faster.

Since the data will be a collection of objects placed to the storage system,
some of the objects will be broken up into multiple pieces by ``plug-ins''
to the system which will allow data to be characterized in terms of the most
important pieces, and the next level of details. We can think of this as
something similar to an Adaptive Mesh Refinement scheme which keeps track of
the places where there are perhaps steep gradients (large errors on the
coarser views), and smaller errors. These then allows us to make decisions
about which sub-objects to save (all of the data, which will then go to
different layers) or just some of the sub-objects? The research questions
are numerous: How does the user specify their intentions? How does the user
prioritize the different sub-objects of the data? Where does the data go
into the storage hierarchy? Does the data get replicated in the lower tiers
of the hierarchy? When the user specifies the time they want the data saved,
how does this get into the storage system?

>>>>

We will examine the research challenges from the perspective of
%
(1) the user of the system who is attempting to run an exascale simulation,
%
(2) the Storage System and I/O layer which needs to negotiate between all of
the users, and finally
%
(3) the user of the system who is attempting to understand the data
produced by a set of simulations.

\subsection{Writing Perspective}
\label{subsec:sim-perspective}
The simulation scientist ideally should be able to
obtain an estimate of how much time will be required to write their data,
and how much storage space they will be able to get during the lifetime of
their simulations. Furthermore, they would like the ability to get an assurance
of Quality of Service such that they can react appropriately when the
expected bandwidth, for example, is less than what they desire. Ideally, the user
would specify a set of rules with which the system can make autonomic
decisions to determine what should be done.
%

One of the key aspects of our approach is to allow the users to define the
utility (importance) of their data; in other-words, for each data object, users
need to come up with a way to define pieces of the object which have more
utility (more importance) . There are many clear research challenges faced with
this approach including: 1) How do we make this simple enough so that users can
do this, 2) can we come up with a model to allow the system to then make the
autonomic decisions to save the data which has the highest utility, and 3) can
we allow the back-end storage system to interact with this definition so that
it can optimize not just over one application but across all of the
applications.
 %
  In our simple scenario, a user wants to write 1 PB of data every hour
for checkpoint/restart, and they wish to write 500TB of data every 15
minutes to save analysis and visualization results which have already been reduced
using in situ reduction techniques. At this stage, they will ask the system to
write their data, and they would like to get an estimated time which they can
then figure out, through a series of rules, whether they want to write out all
of the data, postpone the write until a later time, or write a reduced amount
of data, along with some code
container to allow them to regenerate the data with a specified level of
accuracy.  Furthermore, they realize that the analysis data will be saved on
either the parallel file system, long-term tape storage, or on the campaign storage,
which is a medium-term storage
area with lower bandwidth than the parallel file system.
For each piece of data, the user will specify the lifetime so
that the data with the highest utility is kept around for the longest
period of time, but the data which has the least utility might be migrated to
lower layers of the storage hierarchy more quickly.

Since the data will be a collection of objects placed on the storage system,
some of the objects will be broken up into multiple pieces by ``plug-ins''
to the system which will allow data to be characterized in terms of the most
important pieces, and the next level of details. We can think of this as
something similar to an Adaptive Mesh Refinement scheme which keeps track of
the places where there are perhaps steep gradients (large errors on the
coarser views), and smaller errors. These then allows us to make decisions
about which sub-objects to save (all of the data, which will then go to
different layers) or just some of the sub-objects? The research questions
are numerous: How does the user specify their intentions? How does the user
prioritize the different sub-objects of the data? Where does the data go
into the storage hierarchy? Does the data get replicated in the lower tiers
of the hierarchy? When the user specifies the time they want the data saved,
how does this get into the storage system?
